---
title: "Tableau Dashboard"
output: html_notebook
---

### Visualizing Sales Data

#### Importing packages and data

We start by importing the necessary package for data manipulation and we read the data in CSV file.

```{r}
library(dplyr)
library(lubridate)
sales_data <- read.csv("sales_data.csv")
```

#### Data processing

We use the imported dplyr package to manipulate the data and create new variables for the dashboard.

```{r}
sales_data <- sales_data %>%
  mutate(sale_month = format(ymd(sale_date), "%Y-%m"), 
         product_group = case_when(
           product %in% c("a", "b", "c") ~ "Group A", 
           product %in% c("d", "e", "f") ~ "Group B", 
           product %in% c("g", "h", "i", "j") ~ "Group C"
         ))
```

#### Exporting data

Now we export processed data as a CSV file for visualizations.

```{r}
write.csv(sales_data, "sales_data_cleaned.csv", row.names = FALSE)
```

#### Tableau
We import and connect our cleaned CSV file into tableau public, we create a new worksheet and add the "Sale Month" and "Sales Amount" variables to a line chart and use the "Product Group" variable as a color legend.

We Create a new worksheet and add the "Product Group" and "Sales Amount" variables to a bar chart. Using the "Customer ID" variable as a filter to show only the sales data for a specific customer and then we create a new worksheet and add the "Product" and "Sales Amount" variables to a heat map also using the "Sale Month" variable as a column and the "Product Group" variable as a row.

After the above process then we can finally create a new dashboard and add the three worksheets to it. We also add a filter for the "Sale Month" variable to allow the user to select a specific month.

"Tableau Dashboard" https://public.tableau.com/views/SalesPerformanceDashboard_16829813109670/SalesPerformanceDashboard?:language=en-US&:display_count=n&:origin=viz_share_link
